Total Platform Cyber Protection

### 2016-05-19 paper.tex
Fixed bugs according to Chrisper (bugs in writing)

Another approach is to change the design of the chip to support
runtime monitoring~\cite{Waksman2010}. In this way, the hardware
itself is is monitoring itself, rather than external analysis of
side-channels. However, this has all the same drawbacks of changing
the design of hardware, in addition to not being robust in the face of
a powerful attacker who is able to alter the design.

@@

Trojan capabilities in the firmware itself can allow a system to be
remotely controlled or accessed. This is similar to a vulnerability,
in that an attacker is able to control the firmware, however the key
difference lies in the fact that Trojan behavior will be intentionally
obfuscated by an attacker, whereas a vulnerability is accidentally
introduced by a benign developer. Therefore, Trojan behavior is more
more difficult to detect, because there is an active adversary who is
intentionally obfuscating the behavior.

@@

Another approach has been to include run-time monitoring into the
firmware, so that compromises can be detected~\cite{Cui2010a,
  Cui2011}. This approach is further complicated by the lack of
abstractions in the firmware environment.

@@

Security of the application lays has received significant attention
from the research community. Because of this, we have divided the
research into attack surface reduction, prevent control-flow
hijacking, logic and implementation flaws, mitigation and recovery,
modeling and monitoring execution, and protection against malicious
code.

@@

Significant progress in this area started with the idea of
control-flow integrity, essentially ensuring dynamically at run-time
that the control-flow of the application does not
deviate~\cite{Abadi2005, Abadi2009}. The first implementations were
deemed infeasible, so later research attempted to improve the
efficiency of control-flow integrity~\cite{Zhang2013, Tice2014,
  Bletsch2011, Zhang2013, Zhang2013a}

>>>>

Another approach is to change the design of the chip to support
runtime monitoring~\cite{Waksman2010}. In this way, the hardware
itself is monitoring itself, rather than external analysis of
side-channels. However, this has all the same drawbacks of changing
the design of hardware, in addition to not being robust in the face of
a powerful attacker who is able to alter the design.

@@

Trojan capabilities in the firmware itself can allow a system to be
remotely controlled or accessed. This is similar to a vulnerability,
in that an attacker is able to control the firmware, however the key
difference lies in the fact that Trojan behavior will be intentionally
obfuscated by an attacker, whereas a vulnerability is accidentally
introduced by a benign developer. Therefore, Trojan behavior is 
more difficult to detect, because there is an active adversary who is
intentionally obfuscating the behavior.

@@

Another approach has been to include runtime monitoring into the
firmware, so that compromises can be detected~\cite{Cui2010a,
  Cui2011}. This approach is further complicated by the lack of
abstractions in the firmware environment.

@@

Security of the application layer has received significant attention
from the research community. Because of this, we have divided the
research into the following categories: attack surface reduction, prevent control-flow
hijacking, logic and implementation flaws, mitigation and recovery,
modeling and monitoring execution, and protection against malicious
code.

@@

Significant progress in this area started with the idea of
control-flow integrity, essentially ensuring dynamically at runtime
that the control-flow of the application does not
deviate~\cite{Abadi2005, Abadi2009}. The first implementations were
deemed infeasible, so later research attempted to improve the
efficiency of control-flow integrity~\cite{Zhang2013, Tice2014,
  Bletsch2011, Zhang2013, Zhang2013a}
